### 2015-05-18 implementation.tex
diagrams, implem drivers & OS theory

@@

\lstset{language=c}
\lstset{commentstyle=\color{colComments}\textit,
float=hbp,%
basicstyle=\ttfamily\footnotesize, %
identifierstyle=\color{colIdentifier}, %
keywordstyle=\color{colKeys}, %
stringstyle=\color{colString}, %
columns=flexible, %
tabsize=2, %
extendedchars=true, %
showspaces=false, %
showstringspaces=false, %
numbers=left, %
numberstyle=\tiny, %
breaklines=true, %
breakautoindent=true, %
captionpos=b}
\begin{lstlisting}[caption=openvpn compress then encrypt -- sample from \texttt{forward.c}, label=list:]
/* Compress, fragment, encrypt and HMAC-sign an outgoing packet. */
void encrypt_sign (struct context *c, bool comp_frag)
{
	struct context_buffers *b = c->c2.buffers;
	const uint8_t *orig_buf = c->c2.buf.data;

@@

\subsection{OpenSSL}
% Talk about the debug flags in the compilation and show it has close to none impact on the performance (using openssl speed. openssl speed is a relevant test because openssl uses 100% of the CPU, hence maximizing the potential performance reduction.)

@@

\subsection{Silex engine}

\subsection{BA411E Driver}

\subsection{BA414E Driver}

>>>>

\begin{figure}[ht]
\center
\subfloat[\label{fig:os-path-generic-a}Generic]{%
	\Large
	\resizebox{.4\linewidth}{!}{%
	\input{os-path-generic}
	}
}
\subfloat[\label{fig:os-path-generic-b}Specific]{%
	\Large
	\resizebox{.4\linewidth}{!}{%
	\input{os-path-specific}
	}
}
\caption{OS path generic}
\label{fig:os-path-generic}
\end{figure}

@@

\lstset{language=c}
\lstset{commentstyle=\color{colComments}\textit,
float=hbp,%
basicstyle=\ttfamily\footnotesize, %
identifierstyle=\color{colIdentifier}, %
keywordstyle=\color{colKeys}, %
stringstyle=\color{colString}, %
columns=flexible, %
tabsize=2, %
extendedchars=true, %
showspaces=false, %
showstringspaces=false, %
numbers=left, %
numberstyle=\tiny, %
breaklines=true, %
breakautoindent=true, %
captionpos=b}
\begin{lstlisting}[caption=openvpn compress then encrypt -- sample from \texttt{forward.c}, label=list:openvpn-workflow]
/* Compress, fragment, encrypt and HMAC-sign an outgoing packet. */
void encrypt_sign (struct context *c, bool comp_frag)
{
	struct context_buffers *b = c->c2.buffers;
	const uint8_t *orig_buf = c->c2.buf.data;

@@

\subsection{OpenSSL}

@@

\begin{table}[ht]
\begin{tabular}{|l|c|}\hline
IP & Ciphers \\ \hline
BA414E & RSA, DH, DSA, EC \\ 
BA411E & AES modes CBC, CTR, GCM, CCM, CFB, OFB, CTS, ECB \\ \hline
\end{tabular}
\caption{Summary of the ciphers supported by two of Barco Silex' IPs.}
\label{tab:ip-ciphers}
\end{table}

\subsection{BA411E Driver}
Takes the rightern path, which is the cleanest because the most versatile.
By pluging the driver into the crypto API, we offer a standard kernel interface that can be used by any other kernel driver, such as the ESP driver, or user-space application via the cryptodev driver and OpenSSL engine.

However, at the current state of development, the user-space and the kernel applications do not share the same driver.
The former is using an IRQ-based driver, whilst the latter is actively polling the hardware.
The reason why the IRQ-based driver can not be used by kernel-space application is because the current implementation uses sleep methods that, when called on other kernel drivers, put the kernel in panic mode and require the system to reboot.
An alternative is under development and is further discussed in the last part of this work, in section~\ref{sec:future-work}.

Be it IRQ or polling, the inner workings are the same and follow the exact same canvas as the default software implementation the different AES modes.

\subsection{BA414E Driver and Silex engine}
At the moment of development, there is no asymetric cryptography interface in the crypto API.
The BA414E can thus not be accessed using the same path as the BA411E and a user-space driver will be needed, that is the leftern path of figure~\ref{fig:os-path-generic-b}.
As presented in section~\ref{sec:theory-driver}, we will need to rely on an UIO driver to access the device from the user space.

### 2015-05-18 technical-background.tex
diagrams, implem drivers & OS theory

>>>>

%User/kernel space. Networking application: need to send the data through the kernel: huge overhead.

%Crypto API

\subsection{Device Driver}\label{sec:theory-driver}
% General idea of it works
% device driver in userspace: linux userspace i/o (/dev/mem)
Userspace I/O~\cite{koch2011}

There are two ways to get the results from a hardware device: either by using interruption, or by actively polling the device, relentlessly asking it if it finished its operations.
The first case is the cleanest and the most common: when the device has something to send to the driver, or if anything unexpected happened, it sends an interruption request (IRQ) to the processor, which will in turn execute the interruption routine registered by the driver~\citep[chap. 10]{Corbet:2005:LDD:1209083}.
The second case is the easiest and is always guaranteed to work, but won't let go off the processor willingly, loading it at 100\%, and avoiding any other task to be executed.
Hopefully, modern monolithic kernels such as the Linux kernel from 2.6 provide preemptive scheduling~\cite{Santhanam2003}, that is the scheduler interrupts the running task and assigns the processor ressources it used to an other one.
Hence, systems with a lot of processes in need for CPU ressources would not be stalled, but it would not change anything if the only process heavily requesting processor time is the one using the driver.

\section{FPGA}
